Scalar and Representative Observables for Polarimetric SAR Data

### 2013-10-29 paper_dev/article_pp.tex
changed the figures to allow better view of the axis number
remove x-axis, y-axis label

\newcommand{\plotWithLegend}[2]{          
          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
	    \rput(5,1.5){\footnotesize{#2}}
	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
	    \psline[linecolor=plot](5,8)(6,8)
	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
	    \rput(8,8){\footnotesize{model}}
	    \rput(8,9){\footnotesize{data}}            
          \end{pspicture}
}

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_1d.eps}{determinant}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	} \\
	\subfloat[AIRSAR (HH) determinant ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH) change ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) change ratio]{

\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR dataset homogeneous patches}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

@@

%          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
		 \epsfxsize=1.5in
		 \epsfysize=1.5in

@@

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH-HV-VV) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_3D_determinant}
	} \\
	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_2D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_2D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_2D_change_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
%          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
%	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}% \usebox\IBoxCRThreeR
%	    \rput(5,1.5){\footnotesize{change-ratio}}
%	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
%	    \psline[linecolor=plot](5,8)(6,8)
%	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
%	    \rput(8,8){\footnotesize{model}}
%	    \rput(8,9){\footnotesize{data}}
%          \end{pspicture}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_2D_change_ratio}
	}
\end{tabular}
\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_3D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH-HV-VV) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_change_ratio}
	} \\
	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_3D_determinant}
	}
        \hfill
	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_1D_change_ratio}
	}
\end{tabular}
\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_3D}
\end{figure}
%endif

>>>>

\newcommand{\plotWithLegend}[2]{          
          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
	    %\rput(5,1.5){\footnotesize{#2}}
	    %\rput{90}(1.5,5){\footnotesize{pdf / histogram}}
	    \psline[linecolor=plot](5,8)(6,8)
	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
	    \rput(8,8){\footnotesize{model}}
	    \rput(8,9){\footnotesize{data}}            
          \end{pspicture}
}

@@

%ifdef FINAL
\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_1d.eps}{determinant}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	} \\
	\subfloat[AIRSAR (HH) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	} \\
	\subfloat[AIRSAR (HH) change ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	} 
	\hfill	
	\subfloat[RADARSAT2 (HH) change ratio]{

\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif
%ifdef REVIEW
\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[AIRSAR (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_determinant}
	} 
	\hfill	
	\subfloat[AIRSAR (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}
	\hfill	
	\subfloat[AIRSAR (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
		 \label{AIRSAR_1D_det_ratio}
	}  \\
	\subfloat[RADARSAT2 (HH) determinant]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_determinant}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) determinant ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
        \hfill
        \subfloat[RADARSAT2 (HH) change ratio]{
		 \epsfxsize=2in
		 \epsfysize=2in
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
		 \label{RADARSAT2_1D_det_ratio}
	}
\end{tabular}
\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
\label{fig:verify_POLSAR_model_1D}
\end{figure}
%endif

@@

          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	

@@

\caption{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}

@@

	\subfloat[AIRSAR (HH-HV-VV) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_determinant}
	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_3D_determinant}
	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_2D_change_ratio}
	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
%	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}% \usebox\IBoxCRThreeR
%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_2D_change_ratio}
\caption{The specific $d=3$ models are validated on both RADARSAT2 and AIRSAR datasets.
Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
\label{fig:verify_det_ratio_model_3D}
	\subfloat[AIRSAR (HH-HV-VV) determinant]{
		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_determinant}
	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
		 \label{AIRSAR_3D_change_ratio}
	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_3D_determinant}
	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
		 \label{RADARSAT2_1D_change_ratio}
\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
\label{fig:verify_det_ratio_model_3D}
